Main1

### 2019-11-01 Notes.Rmd
week 1 quiz done

>>>>

"[0-9]+ (.*)[0-9]+" will match, at least one number, followed by whitespace and any number of characters and at least one number again.

- you can quantify the number of repetitions (min and max) you want with the curly brackets{}

"[Bb]ush( +[^ ]+ +){1,5} debate" will match at least one space, followed by something that's not a space, followed by at least one space, and we want to see that between one and five times = we want to see something like space word space.

{m,n} means at least m but not more than n matches
{m} means exactly m matches
{m,} means at least m matches

- in most implementations of regular expressions, the parentheses not only limit the scope of alternatives divided by a "|", but also can be used to "remember" text matched by the subexpression enclosed
we refer to the matched text with \1, \2, etc..

" +([a-zA-Z]+) +\1 +" will match a space, followed by (at least one characters) followed by at least one space, followed by exactly the same match as before.
ex: "............. so so ......."

- * is greedy. it takes the longest possible string. you can use the ? to turn the greediness off.

### 2019-11-01 preproc.Rmd
week 1 quiz done

```{r}
con <- file("./en_US.twitter.txt", "r") 
twit = readLines(con, skipNul = T)
close(con)

@@

>>>>

## twitter files
```{r}
con <- file("./en_US.twitter.txt", "r") 
twit = readLines(con, skipNul = T)
close(con)
y = NULL
for(i in 1:length(twit)) {y[i] = nchar(twit[[i]])}
summary(y)
```

@@

## blogs

```{r}
con <- file("./en_US.blogs.txt", "r") 
blogs = readLines(con, skipNul = T)
close(con)

y = NULL
for(i in 1:length(blogs)) {y[i] = nchar(blogs[[i]])}
summary(y)

set.seed(123)
x = rbinom(899288, size = 1, prob = .7)
#70% of data for training, 30% for testing
train = blog[x]
test = blog[!x]
```
